\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/paper.tex
Remove todo

\TODO{more precise:}
In our scheme (Figure~\ref{fig:highlevel}), clients
request the creation of phantom hosts in the ``dark''
or unused address space of the deploying ISP. Once registered, clients
can connect to these phantom hosts IP addresses as if they were real
proxy servers. The ISP station acts as the other end of these connections, and
responds as if it were a legitimate site or service. To the censor,
these phantom hosts appear as legitimate sites or services, and even
active probes will not reveal information that would allow the censor to
block them.

@@

\scheme involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

\paragraph{Traffic analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme mask site applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

>>>>

%\TODO{more precise:}
In our scheme (Figure~\ref{fig:highlevel}), clients
request the creation of phantom hosts in the ``dark''
or unused address space of the deploying ISP. Once registered, clients
can connect to these phantom hosts IP addresses as if they were real
proxy servers. The ISP station acts as the other end of these connections, and
responds as if it were a legitimate site or service. To the censor,
these phantom hosts appear as legitimate sites or services, and even
active probes will not reveal information that would allow the censor to
block them.

@@

\scheme involves three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

\paragraph{Traffic analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.
